Incremental λ-Calculus in Cache-Transfer Style

### 2017-09-11 popl18/source-language.tex
Remove redundant \noindent

Our syntax for base terms~$\sterm$ represents $\lambda$-lifted
programs in A'-normal form (\cref{sec:motivating-example}).
We write $\many\tx$ for a sequence of variables of some unspecified length
$\tx_1, \tx_2, \ldots, \tx_m$.
A term can be either a bound variable~$\tx$, or a {\bf let}-binding
of~$\ty$ in subterm~$\sterm$ to either a new
tuple~$\stuple{\many\tx}$ ($\slet{\ty = \stuple{\many\tx}}\sterm$), or
the result of calling function~$\tf$ on argument~$\tx$
($\slet{\ty = \sapp{\tf}{\tx}}{\sterm}$). Both~$\tf$ and~$\tx$ are
variables to be looked up in the environment. Terms cannot contain
$\lambda$-abstractions as they have been $\lambda$-lifted to top-level
definitions, which we encode as closures in the initial environments.
%
Unlike standard ANF we add no special syntax for function
calls in tail position (see \cref{sec:tail-calls} for a discussion
about this limitation).
%
We often inspect the result of
a function call~$\tf\,\tx$, which is not a valid term in our syntax.
To enable this, we write~``$\scall\tf\tx$''
for ``$\slet{\ty = \tf\;\tx}\ty$'' where $\ty$ is
chosen fresh.

>>>>

Our syntax for base terms~$\sterm$ represents $\lambda$-lifted
programs in A'-normal form (\cref{sec:motivating-example}).
We write $\many\tx$ for a sequence of variables of some unspecified length
$\tx_1, \tx_2, \ldots, \tx_m$.
A term can be either a bound variable~$\tx$, or a {\bf let}
binding of $\ty$ in subterm~$\sterm$ to either a new
tuple~$\stuple{\many\tx}$ ($\slet{\ty = \stuple{\many\tx}}\sterm$), or
the result of calling function~$\tf$ on argument~$\tx$
($\slet{\ty = \sapp{\tf}{\tx}}{\sterm}$).  Both~$\tf$ and~$\tx$ are
variables to be looked up in the environment.  Terms cannot contain
$\lambda$-abstractions as they have been $\lambda$-lifted to top-level
definitions, which we encode as closures in the initial environments.
%
Unlike standard ANF we add no special syntax for function
calls in tail position (see \cref{sec:tail-calls} for a discussion
about this limitation).
%
We often inspect the result of
a function call~$\tf\,\tx$, which is not a valid term in our syntax.
To enable this, we write~``$\scall\tf\tx$''
for ``$\slet{\ty = \tf\;\tx}\ty$'' where $\ty$ is
chosen fresh.
